The Galaxy Cluster Merger Catalog: An Online Repository of Mock Observations from Simulated Galaxy Cluster Mergers

### 2016-09-13 paper/ms.tex
Added some more material to the summary

We have made the first release of the ``Galaxy Cluster Merger Catalog'', a website designed to provide a simple yet powerful interface to accessing mock observations of galaxy cluster mergers.

@@

\begin{itemize}
\item Adding cluster merger simulations from other research groups, especially those from cosmlogical simulations
\item Adding mock observations from other wavebands, such as radio and optical
\item Adding additional lines of sight through the simulation domain
\item Implementing more ways to interact with the data, such as Jupyter notebooks that may be run on the server
\item Adding other types of data products, including movies, unconvolved X-ray event lists, and the original 3D datasets
\end{itemize}

>>>>

We have made the first release of the ``Galaxy Cluster Merger Catalog'', a website designed to provide a simple yet powerful interface to accessing mock observations of galaxy cluster mergers. This release includes a suite of mock observations from a number of binary cluster merger simulations, with different initial conditions and input physics. In particular, the catalog provides a number of X-ray and S-Z synthetic observations as well as mock galaxy catalogs. Projections of the observables have been taken along a number of lines of sight through the simulation box, and at a large number of epochs for each simulation so that the merger history is well-sampled in time. This large parameter space of cluster mergers will be useful when comparing with observed cluster mergers in a number of wavebands.

@@

\begin{itemize}
\item Adding cluster merger simulations from other research groups, especially those from cosmlogical simulations
\item Adding mock observations from other wavebands, such as radio and optical
\item Adding additional lines of sight through the simulation domain
\item Implementing more ways to interact with the data, such as Jupyter notebooks that may be run on the server
\item Adding other types of data products, including movies, unconvolved X-ray event lists, and the original 3D datasets
\item Providing example scripts to show other researchers how to generate similar data products from their simulations
\end{itemize}
